### 2023-09-20 main.tex
rty

We will exploit the duality and the underlying symmetries of the model, to write explicitly all the correlations of this \textit{hard-core exclusion} case. The main tool that we will use is the Lie algebraic description of the process, that allows to find the duality as a proper symmetry of the generator. 

@@

The average with respect to the non equilibrium distribution of the occupation variable of the species $a_{1}\in \{1,\ldots,N-1\}$ at coordinate $y_{1}\in \{1,\ldots,L\}$ reads
	\langle n_{a_{1}}^{y_{1}}\rangle_{\text{stat}}=\sum_{c_{1}=0}^{1}f(L,c_{1})(\alpha_{a_{1}}-\beta_{a_{1}})^{c_{1}}\beta_{a_{1}}^{1-c_{1}}g_{a_{1}}(L,y_{1},c_{1})

@@

\langle n_{a_{1}}^{y_{1}}\rangle_{\text{stat}}=\frac{(L+1-y_{1})}{L+1}(\alpha_{a_{1}}-\beta_{a_{1}})+\beta_{a_{1}}

@@

The two points correlations with respect the non equilibrium distribution of the occupation variable of the species $a_{1},a_{2}\in \{1,\ldots,N-1\}$ at coordinates $x_{1},x_{2}\in \{1,\ldots,L\}$ with $x_{1}< x_{2}$ reads 
	\langle n_{a_{1}}^{y_{1}}n_{a_{2}}^{y_{2}}\rangle_{\text{stat}}= \sum_{c_{1}=0}^{1}\sum_{c_{2}=0}^{1}f(L,c_{1},c_{2})\prod_{k=1}^{2}(\alpha_{a_{k}}-\beta_{a_{k}})^{c_{k}}\beta_{a_{k}}^{1-c_{k}}g_{k}(L,y_{k},c_{k},c_{2})

@@

	\langle n_{a_{1}}^{y_{2}} n_{a_{2}}^{y_{2}}\rangle_{\text{stat}}&=\beta_{a_{1}}\beta_{a_{2}}+\frac{(L+1-y_{1})}{L+1}(\alpha_{a_{1}}-\beta_{a_{1}})\beta_{a_{2}}+\frac{(L+1-y_{2})}{L+1}(\alpha_{a_{2}}-\beta_{a_{2}})\beta_{a_{1}}\\&+\frac{(L-y_{1})(L+1-y_{2})}{L(L+1)}(\alpha_{a_{1}}-\beta_{a_{1}})(\alpha_{a_{2}}-\beta_{a_{2}})

@@

		\langle n_{a_{1}}^{y_{2}} n_{a_{2}}^{y_{2}}\rangle_{\text{stat}}^{c}=\mathbb{E}[n_{a_{1}}^{y_{1}}n_{a_{2}}^{y_{2}}]-\mathbb{E}[n_{a_{1}}^{y_{1}}]\mathbb{E}[n_{a_{2}}^{y_{2}}]=-\frac{x_{1}(L-y_{2}+1)}{L(L+1)^{2}}\left(\alpha_{a_{1}}-\beta_{a_{1}}\right)\left(\alpha_{a_{2}}-\beta_{a_{2}}\right)

@@

The three points correlations with respect the non equilibrium distribution of the occupation variable of the species $a_{1},a_{2},a_{3}\in \{1,\ldots,N-1\}$ at coordinates $y_{1},y_{2},y_{3}\in \{1,\ldots,L\}$ such that $y_{1}<y_{2}<y_{3}$
    \langle n_{a_{1}}^{y_{1}}n_{a_{2}}^{y_{2}}n_{a_{3}}^{y_{3}}\rangle_{\text{stat}}=\sum_{c_{1}=0}^{1}\sum_{c_{2}=0}^{1}\sum_{c_{3}=0}^{1}f(L,c_{1},c_{2},c_{3})\prod_{k=1}^{2}(\alpha_{a_{k}}-\beta_{a_{k}})^{c_{k}}\beta_{a_{k}}^{1-c_{k}}g_{k}(L,y_{k},c_{k},\ldots,c_{3})

@@

        \langle n_{a_{1}}^{y_{1}}n_{a_{2}}^{y_{2}}n_{a_{3}}^{y_{3}}\rangle_{\text{stat}}&=\beta_{a_{1}}\beta_{a_{2}}\beta_{a_{3}}+\frac{(L+1-y_{1})}{(L+1)}(\alpha_{a_{1}}-\beta_{a_{1}})\beta_{a_{2}}\beta_{a_{3}}

@@

        \frac{(L+1-y_{2})}{(L+1)}(\alpha_{a_{2}}-\beta_{a_{2}})\beta_{a_{1}}\beta_{a_{3}}+\frac{(L+1-y_{3})}{(L+1)}(\alpha_{a_{3}}-\beta_{a_{3}})\beta_{a_{1}}\beta_{a_{2}}

@@

        \frac{(L-x_{2})(L-y_{3}+1)}{L(L+1)}(\alpha_{a_{2}}-\beta_{a_{2}})(\alpha_{a_{3}}-\beta_{a_{3}})\beta_{a_{1}}

@@

        \frac{(L-y_{1})(L-y_{3}+1)}{L(L+1)}(\alpha_{a_{1}}-\beta_{a_{1}})(\alpha_{a_{3}}-\beta_{a_{3}})\beta_{a_{2}}

@@

        \frac{(L-y_{1})(L-y_{2}+1)}{L(L+1)}(\alpha_{a_{1}}-\beta_{a_{1}})(\alpha_{a_{2}}-\beta_{a_{2}})\beta_{a_{3}}

@@

        \frac{(L-y_{1}-1)(L-y_{2})(L-y_{3}+1)}{L(L-1)(L+1)}(\alpha_{a_{1}}-\beta_{a_{1}})(\alpha_{a_{2}}-\beta_{a_{2}})(\alpha_{a_{3}}-\beta_{a_{3}})

@@

	\langle n_{a_{1}}^{y_{1}}n_{a_{2}}^{y_{2}}n_{a_{3}}^{y_{3}}\rangle_{stat}^{c}&=\mathbb{E}\left[n_{a_{1}}^{y_{1}}n_{a_{2}}^{y_{2}}\right]-\mathbb{E}\left[n_{a_{1}}^{y_{1}}n_{a_{2}}^{y_{2}}\right]\mathbb{E}\left[n_{a_{3}}^{y_{3}}\right]-\mathbb{E}\left[n_{a_{1}}^{y_{1}}n_{a_{3}}^{y_{3}}\right]\mathbb{E}\left[n_{a_{2}}^{y_{2}}\right]\\&-\mathbb{E}\left[n_{a_{3}}^{y_{3}}n_{a_{2}}^{y_{2}}\right]\mathbb{E}\left[n_{a_{1}}^{y_{1}}\right]+2\mathbb{E}\left[n_{a_{1}}^{y_{1}}\right]\mathbb{E}\left[n_{a_{2}}^{y_{2}}\right]\mathbb{E}\left[n_{a_{3}}^{y_{3}}\right]
	-\frac{2y_{1}(L+1-2y_{2})(L+1-y_{3})}{(L+1)^{3}(L-1)L}(\alpha_{a_{1}}-\beta_{a_{1}})(\alpha_{a_{2}}-\beta_{a_{2}})(\alpha_{a_{3}}-\beta_{a_{3}})

@@

In Subsection \ref{subsection-exact}, we have found two similarity transformations, namely $S_{1}$ and $S_{2}$, that map the original Hamiltonian $H$ onto a simpler one $H^{''}$, that although non-stochastic, allows to compute the explicit expression of the steady state correlations. To complete the picture, in this section we aim to find a further similarity transformation, called $W$, that maps $H^{''}$ onto $H_{0}$ that will be defined as the original Hamiltonian where the boundaries are set diagonal. These boundaries do not produce any current and thus $H_{0}$ is called \textit{equilibrium Hamiltonian}. For this reason, we say that the process is mapped onto equilibrium, indeed, using the sequence of transformations one can go from non-equilibrium to equilibrium and back.

@@

 We denote by $\bm{m}=(m_{1},\ldots,m_{N})$ an $N-$dimensional vector where each $m_{i}=\sum_{x=1}^{L}n_{i}^{x}$, i.e. it means the total occupation over the chain of each species $i\in\{1,\ldots,N\}$. Observe that $|\bm{m}|=\sum_{i=1}^{N}m_{i}=L$. We call $\mathcal{E}_{\bm{m}}$ and $|\Psi_{\bm{m}}^{0}\rangle$ the eigenvalue and the eigenvector of $H^{0}$ that correspond to a certain $\bm{m}$. We prove that 

@@

In order to be well defined $z$ must not be an eigenvalue of $H^{''}$. Fix with $\epsilon>0$ and arbitrary, then we chose $z=\mathcal{E}_{\bm{m}}+\epsilon$, 

@@

we sum over all possible $\bm{m}$'s 
	\sum_{\bm{m}\,:\, |\bm{m}|=L}  (\mathcal{E}_{\bm{m}}+\epsilon-H^{''})R(H^{''},\Lambda_{m}+\epsilon)|\Psi_{m}^{0}\rangle \langle \Psi_{m}^{0}|=\sum_{\bm{m}\,:\, |\bm{m}|=L}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|,
we multiply both sides by $\epsilon$ 
	\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}  (\mathcal{E}_{\bm{m}}+\epsilon-H^{''})R(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{m}^{0}|=\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|,
we take the limit for $\epsilon\to 0$ on both sides 

@@

Observe that, trivially,

@@

and using the following power expansion

@@

we have that for each $\bm{m}$ 

@@

therefore the limit of the product is the product of the limit and we obtain that 

@@

Since the limit of the sum is the sum of the limit we have   

@@

thus 

@@

Formula \eqref{W-extended} may be evaluated by perturbation theory. Moreover, since the process is integrable it is possible to express $W$ in function of the conserved charges of the system and of the eigenvectors of the equilibrium steady state, that are known in literature by Bethe ansatz. This expression, as it will be shown in the following sections, allows a simpler treatment of the mapping and furthermore we can use it to retrieve the steady state of $H^{''}$ by applying $W$ to the ground state of $H_{0}$. To write formula \eqref{W-extended} using the conserved charges of the system, we use Quantum Inverse Scattering Method (QISM). This will be presented in Subsection \ref{SubsectionQISM}. In Subsection \ref{SubsectionGL2} we first present the simpler case of $gl(2)$, then, in Subsection \ref{SubsectionGLN} we adapt the proof to the general $gl(N)$. 

@@

where the lower index $a$ means that they are written in the canonical basis of the space $V_{a}=\mathbb{C}^{N}$, for $a\in\{0,\ldots,L\}$ and where $x,y\in\mathbb{C}$ are called spectral parameters.  

@@

The double row monodromy $U_{0}(x)$ is given by

@@

We write $U_{0}(x)$ in the canonical basis of $V_{0}$ and we rename its elements, each of them acting on the quantum space $V$, has follows

@@

@@

The exchange relations for the elements of the above matrix can be found using \eqref{RURU} and they read:

@@

The transfer matrix $T^{\Delta}(x)$ reads
		T^{\Delta}(x)=%tr_{0}&\left(\begin{pmatrix}

@@

By construction,$T(x)$ is a polynomial in $x$ with exponents from $0$ to $2L+2$ 

@@

where, for all $k\in\{0,\ldots,2L+2\}$, we call $Q_{k}$ the \textit{conserved charges} of the system. We also introduce 

@@

Arguing similarly we write the elements of $U_{0}(x)$ in a polynomial expansion as 
	D_{N,N}(x)=\sum_{a=0}^{2L+1}D_{N,N}^{a}x^{a}\quad D_{ii}(x)=\sum_{a=0}^{2L+1}D_{ii}^{a}x^{a}\quad B_{i}(x)=\sum_{a=0}^{2L-1}B_{i}^{a}x^{a}\quad D_{i,j}(x)=\sum_{a=0}^{2L}D_{i,j}^{a}x^{a}
 In the following we will study the charge expansion of $T^{\Delta}(x)$ when $x\to \infty$. As it will be clear in the following, only the first three coefficients for the diagonal elements and only the first one for the non-diagonal elements will be needed. Therefore, using \eqref{RURU}, we compute: 

@@

\begin{equation}
	D_{N,N}^{2L+1}=I^{tot}
\end{equation}
\begin{equation}\label{DNN-charge}
	D_{N,N}^{2L}=I^{tot}+2e_{NN}^{tot}
\end{equation}
\begin{equation}
	D_{N,N}^{2L-1}	=2e_{NN}^{tot}\left(e_{NN}^{tot}+I^{tot}\right)-L
\end{equation}

@@

\item For $D_{i,j}(x)$ with $i,j=2,\ldots,N$ such that $i\neq j$
\begin{equation}\label{Dij-Charge}
D_{i,j}^{2L}=-2e_{ji}^{tot}
\end{equation}
\end{itemize}
\textbf{Remark}: it is easy to see that, when restricted to the case of 2 species,  we obtain equations (2.24)-(2.30) of \cite{frassek2020eigenstates}. \\ \\
Using these polynomial expansions we write the first three charges

\begin{align}
Q_{2L+2}&=D_{N,N}^{2L+1}-\sum_{i=1}^{N-1}D_{ii}^{2L+1}=N
\end{align}
\begin{align}
Q_{2L+1}&=ND_{N,N}^{2L+1}+A^{2L}-\sum_{i=1}^{N-1}D_{ii}^{2L}=N+2L-1
\end{align}
\begin{align}
Q_{2L\phantom{+}}&=ND_{N,N}^{2L}+D_{N,N}^{2L-1}-\sum_{i=1}^{N-1}D_{ii}^{2L-1}+\sum_{i=1}^{N-1}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}
\end{align}
The charges $Q_{2L+2}$ and $Q_{2L+1}$ are proportional to the identity matrix, while $Q_{2L}$ contains non diagonal matrices and the boundary parameters $\alpha_{i},\beta_{i}$ $\forall i=2,\ldots,N$.\\
By construction it follows that 
\begin{equation}
\left[Q_{2L},H^{''}\right]=Q_{2L}H^{''}-H^{''}Q_{2L}=0
\end{equation}
The commutation with the Hamiltonian $H^{''}$ for $Q_{2L+2}$ and $Q_{2L+1}$ is trivial. \\
We introduce the following:
\begin{equation}
Q_{2L}^{0}:=ND_{N,N}^{2L}+D_{N,N}^{2L-1}-\sum_{i=1}^{N-1}D_{ii}^{2L-1}
\end{equation}
that is, using the coefficients previously computed, 
\begin{equation}\label{Q0Exp}
\begin{split}
Q_{2L}^{0}=(N-NL-2L)I^{tot}+2(N+2)e_{NN}^{tot}+2e_{NN}^{tot}e_{NN}^{tot}+2\sum_{j,k=1}^{N-1}e_{kj}^{tot}e_{jk}^{tot}
\end{split}
\end{equation}

We also introduce 
\begin{equation}\label{Q-nonDiag}
\mathcal{Q}_{2L}=\sum_{i=1}^{N-1}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}=\sum_{i=1}^{N-1}2\Delta_{i}B_{i}^{2L-1}
\end{equation}
where $\Delta_{i}=(\alpha_{i}-\beta_{i})$. 
Therefore we can write 
\begin{equation}
Q_{2L}=Q_{2L}^{0}+\mathcal{Q}_{2L}
\end{equation}
Observe that $Q_{2L}$ and $Q_{2L}^{0}$ are isospectral. \\
%  It has the property that commute with the equilibrium Hamiltonian.

Consider the matrix $Q_{0}^{2L}$ defined in \eqref{Q0Exp}. All terms are diagonal except the last one. This last non-diagonal can be identified with the second Casimir of the $gl(N-1)$ subalgebra. We denote it by $\hat{C}_{2}^{N-1}$ and it reads

@@

We denote its eigenvector by $C_{2}^{N-1}$. Since the configuration space of the process is given by the tensor product of the first fundamental representation of $gl(N)$, we can decompose it in a direct sum of irreducible representation of $gl(N)$. The Bethe states belong to the configurations space, and thus we can write them as a direct sum of vectors, each belonging to an irreducible representation of $gl(N)$. On these irreducible vectors . $\hat{C}_{2}^{N-1}$ acts diagonally with eigenvalues $C_{2}^{N-1}$ given in terms of shifted weights, i.e. 

@@

\\&=N x^{2L+2}+2(N+1) x^{2L+1}+ \left(N+2m_1(m_1+1)-(N+2)(L-m_1)+2C_{2}^{N-1}\right)x^{2L}+\ldots

@@

\paragraph{Exchange relations between charges}
Using \eqref{EX1}, \eqref{EX2}, \eqref{EX3}, \eqref{EX4},\eqref{EX5} and \eqref{EX6} we obtain for every $i,j\in\{1,\ldots,N-1\}$ 

@@

While, for $i,j,k\in\{1,\ldots,N-1\}$ such that $i\neq j$, $k\neq i,h$

@@

By using the QISM results found in the previous section it is possible to rewrite $W$ in function of first non-trivial conserved charges of the system. This is possible because, thanks to integrability

@@

and moreover $T(x)=\sum_{a=0}^{2L}Q^{2L}x^{a}$ with the property that, the first non-diagonal charge $Q^{2L}$ commutes with $H^{''}$ and thus we can look for a matrix $W$ such that 

>>>>

We will exploit the duality and the underlying symmetries of the model, to write explicitly all the correlations of this \textit{hard-core exclusion} case. The main tool that we will use is the Lie algebraic description of the process, that allows to find the duality as a proper symmetry of the generator. \\
 For a complete review of the quantum inverse scattering method see \cite{Sklyanin:1988yz} and \cite{faddeev1996algebraic}. For application of the QISM to interacting particle systems we refer to \cite{frassek2020eigenstates,frassek2019non,frassek2022exact,vanicat2017exact}. \\

@@

The average with respect to the non equilibrium distribution of the occupation variable of the species $s_{1}\in \{1,\ldots,N-1\}$ at coordinate $y_{1}\in \{1,\ldots,L\}$ reads
	\langle n_{s_{1}}^{y_{1}}\rangle_{\text{stat}}=\sum_{c_{1}=0}^{1}f(L,c_{1})(\alpha_{s_{1}}-\beta_{s_{1}})^{c_{1}}\beta_{s_{1}}^{1-c_{1}}g_{s_{1}}(L,y_{1},c_{1})

@@

\langle n_{s_{1}}^{y_{1}}\rangle_{\text{stat}}=\frac{(L+1-y_{1})}{L+1}(\alpha_{s_{1}}-\beta_{s_{1}})+\beta_{s_{1}}

@@

The two points correlations with respect the non equilibrium distribution of the occupation variable of the species $s_{1},s_{2}\in \{1,\ldots,N-1\}$ at coordinates $x_{1},x_{2}\in \{1,\ldots,L\}$ with $x_{1}< x_{2}$ reads 
	\langle n_{a_{1}}^{y_{1}}n_{a_{2}}^{y_{2}}\rangle_{\text{stat}}= \sum_{c_{1}=0}^{1}\sum_{c_{2}=0}^{1}f(L,c_{1},c_{2})\prod_{k=1}^{2}(\alpha_{s_{k}}-\beta_{s_{k}})^{c_{k}}\beta_{s_{k}}^{1-c_{k}}g_{k}(L,y_{k},c_{k},c_{2})

@@

	\langle n_{s_{1}}^{y_{2}} n_{s_{2}}^{y_{2}}\rangle_{\text{stat}}&=\beta_{s_{1}}\beta_{s_{2}}+\frac{(L+1-y_{1})}{L+1}(\alpha_{s_{1}}-\beta_{s_{1}})\beta_{s_{2}}+\frac{(L+1-y_{2})}{L+1}(\alpha_{s_{2}}-\beta_{s_{2}})\beta_{s_{1}}\\&+\frac{(L-y_{1})(L+1-y_{2})}{L(L+1)}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{2}}-\beta_{s_{2}})

@@

		\langle n_{s_{1}}^{y_{2}} n_{s_{2}}^{y_{2}}\rangle_{\text{stat}}^{c}=\mathbb{E}[n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}]-\mathbb{E}[n_{s_{1}}^{y_{1}}]\mathbb{E}[n_{s_{2}}^{y_{2}}]=-\frac{x_{1}(L-y_{2}+1)}{L(L+1)^{2}}\left(\alpha_{s_{1}}-\beta_{s_{1}}\right)\left(\alpha_{s_{2}}-\beta_{s_{2}}\right)

@@

The three points correlations with respect the non equilibrium distribution of the occupation variable of the species $s_{1},s_{2},s_{3}\in \{1,\ldots,N-1\}$ at coordinates $y_{1},y_{2},y_{3}\in \{1,\ldots,L\}$ such that $y_{1}<y_{2}<y_{3}$
    \langle n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}n_{s_{3}}^{y_{3}}\rangle_{\text{stat}}=\sum_{c_{1}=0}^{1}\sum_{c_{2}=0}^{1}\sum_{c_{3}=0}^{1}f(L,c_{1},c_{2},c_{3})\prod_{k=1}^{2}(\alpha_{s_{k}}-\beta_{s_{k}})^{c_{k}}\beta_{s_{k}}^{1-c_{k}}g_{k}(L,y_{k},c_{k},\ldots,c_{3})

@@

        \langle n_{a_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}n_{s_{3}}^{y_{3}}\rangle_{\text{stat}}&=\beta_{s_{1}}\beta_{s_{2}}\beta_{s_{3}}+\frac{(L+1-y_{1})}{(L+1)}(\alpha_{s_{1}}-\beta_{s_{1}})\beta_{s_{2}}\beta_{s_{3}}

@@

        \frac{(L+1-y_{2})}{(L+1)}(\alpha_{s_{2}}-\beta_{s_{2}})\beta_{s_{1}}\beta_{s_{3}}+\frac{(L+1-y_{3})}{(L+1)}(\alpha_{s_{3}}-\beta_{s_{3}})\beta_{s_{1}}\beta_{s_{2}}

@@

        \frac{(L-x_{2})(L-y_{3}+1)}{L(L+1)}(\alpha_{s_{2}}-\beta_{s_{2}})(\alpha_{s_{3}}-\beta_{s_{3}})\beta_{s_{1}}

@@

        \frac{(L-y_{1})(L-y_{3}+1)}{L(L+1)}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{3}}-\beta_{s_{3}})\beta_{s_{2}}

@@

        \frac{(L-y_{1})(L-y_{2}+1)}{L(L+1)}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{2}}-\beta_{s_{2}})\beta_{s_{3}}

@@

        \frac{(L-y_{1}-1)(L-y_{2})(L-y_{3}+1)}{L(L-1)(L+1)}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{2}}-\beta_{s_{2}})(\alpha_{s_{3}}-\beta_{s_{3}})

@@

	\langle n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}n_{s_{3}}^{y_{3}}\rangle_{stat}^{c}&=\mathbb{E}\left[n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}\right]-\mathbb{E}\left[n_{s_{1}}^{y_{1}}n_{s_{2}}^{y_{2}}\right]\mathbb{E}\left[n_{s_{3}}^{y_{3}}\right]-\mathbb{E}\left[n_{s_{1}}^{y_{1}}n_{s_{3}}^{y_{3}}\right]\mathbb{E}\left[n_{s_{2}}^{y_{2}}\right]\\&-\mathbb{E}\left[n_{s_{3}}^{y_{3}}n_{s_{2}}^{y_{2}}\right]\mathbb{E}\left[n_{s_{1}}^{y_{1}}\right]+2\mathbb{E}\left[n_{s_{1}}^{y_{1}}\right]\mathbb{E}\left[n_{s_{2}}^{y_{2}}\right]\mathbb{E}\left[n_{s_{3}}^{y_{3}}\right]
	-\frac{2y_{1}(L+1-2y_{2})(L+1-y_{3})}{(L+1)^{3}(L-1)L}(\alpha_{s_{1}}-\beta_{s_{1}})(\alpha_{s_{2}}-\beta_{s_{2}})(\alpha_{s_{3}}-\beta_{s_{3}})

@@

In Section \ref{sectionIntegrabiliy}, we have found two similarity transformations, namely $S_{1}$ and $S_{2}$, that map the original Hamiltonian $H$ onto a simpler one $H^{''}$, that although non-stochastic, allows to compute the explicit expression of the steady state correlations. To complete the picture, in this section we aim to find a further similarity transformation, called $W$, that maps $H^{''}$ onto $H_{0}$ that will be defined as the original Hamiltonian where the boundaries are set diagonal. These boundaries do not produce any current and thus $H_{0}$ is called \textit{equilibrium Hamiltonian}. For this reason, we say that the process is mapped onto equilibrium, indeed, using the sequence of transformations one can go from non-equilibrium to equilibrium and back.

@@

 We denote by $\bm{m}=(m_{1},\ldots,m_{N})$ an $N-$dimensional vector where each $m_{i}=\sum_{x=1}^{L}n_{i}^{x}$, i.e. $m_{i}$ indicates the total occupation over the chain of each species $i\in\{1,\ldots,N\}$. Observe that $|\bm{m}|=\sum_{i=1}^{N}m_{i}=L$. We denote by $\mathcal{E}_{\bm{m}}$ and $|\Psi_{\bm{m}}^{0}\rangle$ the eigenvalue and the eigenvector of $H^{0}$ that correspond to a certain $\bm{m}$. We prove that 

@@

In order to be well defined $z$ must not be an eigenvalue of $H^{''}$. Fix an arbitrary $\epsilon>0$ and consider $z=\mathcal{E}_{\bm{m}}+\epsilon$, 

@@

by summing over all possible $\bm{m}$'s such that $|\bm{m}|=L$ and multiply by $\epsilon$ both sides
%	\sum_{\bm{m}\,:\, |\bm{m}|=L}  (\mathcal{E}_{\bm{m}}+\epsilon-H^{''})R(H^{''},\Lambda_{m}+\epsilon)|\Psi_{m}^{0}\rangle \langle \Psi_{m}^{0}|=\sum_{\bm{m}\,:\, |\bm{m}|=L}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|,
%we multiply both sides by $\epsilon$ 
	\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}  (\mathcal{E}_{\bm{m}}+\epsilon-H^{''})R(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{m}^{0}|=\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|.
We take the limit for $\epsilon\to 0$ on both sides 

@@

We first observe that

@@

Second, using the power expansion

@@

we have that, for each $\bm{m}$, 

@@

Since both factor are finite, the limit of the product is the product of the limit and we obtain

@@

Since the limit of the sum is the sum of the limit   

@@

Recalling that $|\Psi_{\bm{m}}^{0}\rangle$ are the eigenvectors with eigenvalue $\mathcal{E}_{\bm{m}}$ of $H_{0}$ we have 

@@

Formula \eqref{W-extended} may be evaluated by perturbation theory (see \cite{frassek2020duality}). Moreover, since the process is integrable it is possible to express $W$ in function of the conserved charges of the system. This expression allows a simpler treatment of the mapping and allows also to retrieve the steady state of $H^{''}$ by applying $W$ to the ground state of $H_{0}$. To write formula \eqref{W-extended} through the conserved charges of the system, we use Quantum Inverse Scattering Method (QISM) (see \ref{SubsectionQISM}). In Subsection \ref{SubsectionGL2} we first construct $W$ for the simpler case of $gl(2)$, then, in Subsection \ref{SubsectionGLN} we adapt the proof to the general $gl(N)$. 

@@

where the lower index $a\in\{0,\ldots,L\}$ means that these matrices are written in the canonical basis of the space $V_{a}=\mathbb{C}^{N}$. Variables $x,y\in\mathbb{C}$ are called spectral parameters.  

@@

The matrix $U_{0}(x)$ used to construct $T(x)$ is called double row monodromy and it is given by

@@

 $U_{0}(x)$ can be written in the canonical basis of $V_{0}$ 

@@

\begin{equation}\label{matrixForm-U}

@@

where each of the above element acts on the quantum space $V$. These element satisfy some \textit{exchange relations} that can be found by \eqref{RURU} and they are given by: 

@@

Using the matrix form of $U_{0}(x)$ written in \eqref{matrixForm-U}, the transfer matrix $T(x)$ reads
		T(x)=%tr_{0}&\left(\begin{pmatrix}

@@

By construction, $T(x)$ is a polynomial in $x$ with exponents from $0$ to $2L+2$, i.e. 

@@

where, for all $k\in\{0,\ldots,2L+2\}$, we call the matrices $Q_{k}$ the \textit{conserved charges} of the system. We also introduce 

@@

Arguing similarly we write the elements of $U_{0}(x)$  as polynomials in $x$ as 
	D_{N,N}(x)=\sum_{k=0}^{2L+1}D_{N,N}^{k}x^{k}\quad D_{i,i}(x)=\sum_{k=0}^{2L+1}D_{i,i}^{k}x^{k}\quad B_{i}(x)=\sum_{k=0}^{2L-1}B_{i}^{k}x^{k}\quad D_{i,j}(x)=\sum_{k=0}^{2L}D_{i,j}^{k}x^{k}
 In the following we will need the charge expansion of $T(x)$. As it will be clear in the following, only the first three coefficients for the diagonal elements of $U_{0}(x)$ and only the first one for the non-diagonal elements of $U_{0}(x)$ will be needed. Therefore, using \eqref{RURU}, we compute: 

@@

	D_{N,N}^{2L+1}=I^{tot}
\begin{equation}\label{DNN-charge}
	D_{N,N}^{2L}=I^{tot}+2e_{NN}^{tot}
	D_{N,N}^{2L-1}	=2e_{NN}^{tot}\left(e_{NN}^{tot}+I^{tot}\right)-L

@@

\item For $D_{i,j}(x)$ with $i,j=2,\ldots,N$ such that $i\neq j$
\begin{equation}\label{Dij-Charge}
D_{i,j}^{2L}=-2e_{ji}^{tot}
\end{equation}
\end{itemize}
\textbf{Remark}: when restricted to the case of 2 species, we obtain equations (2.24)-(2.30) of \cite{frassek2020eigenstates}. \\ \\
Using these polynomial expansions we write the first three charges

\begin{align}
Q_{2L+2}&=D_{N,N}^{2L+1}-\sum_{i=1}^{N-1}D_{ii}^{2L+1}=N
\end{align}
\begin{align}
Q_{2L+1}&=ND_{N,N}^{2L+1}+A^{2L}-\sum_{i=1}^{N-1}D_{ii}^{2L}=N+2L-1
\end{align}
\begin{align}
Q_{2L\phantom{+}}&=ND_{N,N}^{2L}+D_{N,N}^{2L-1}-\sum_{i=1}^{N-1}D_{ii}^{2L-1}+\sum_{i=1}^{N-1}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}
\end{align}
The charges $Q_{2L+2}$ and $Q_{2L+1}$ are proportional to the identity matrix, while $Q_{2L}$ contains non diagonal matrices and the boundary parameters $\alpha_{i},\beta_{i}$ $\forall i=1,\ldots,N-1$.\\
By construction it follows that 
\begin{equation}
\left[Q_{2L},H^{''}\right]=Q_{2L}H^{''}-H^{''}Q_{2L}=0
\end{equation}
while the commutation with the Hamiltonian $H^{''}$ for $Q_{2L+2}$ and $Q_{2L+1}$ is trivial. We introduce the following matrix:
\begin{equation}
Q_{2L}^{0}:=ND_{N,N}^{2L}+D_{N,N}^{2L-1}-\sum_{i=1}^{N-1}D_{ii}^{2L-1}
\end{equation}
that is, using the coefficients previously computed, 
\begin{equation}\label{Q0Exp}
\begin{split}
Q_{2L}^{0}=(N-NL-2L)I^{tot}+2(N+2)e_{NN}^{tot}+2e_{NN}^{tot}e_{NN}^{tot}+2\sum_{j,k=1}^{N-1}e_{kj}^{tot}e_{jk}^{tot}
\end{split}
\end{equation}

We also introduce 
\begin{equation}\label{Q-nonDiag}
\mathcal{Q}_{2L}=\sum_{i=1}^{N-1}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}=\sum_{i=1}^{N-1}2\Delta_{i}B_{i}^{2L-1}
\end{equation}
where, for the sake of notation we denoted $\Delta_{i}=(\alpha_{i}-\beta_{i})$. Therefore we can write 
\begin{equation}
Q_{2L}=Q_{2L}^{0}+\mathcal{Q}_{2L}
\end{equation}
Observe that $Q_{2L}$ and $Q_{2L}^{0}$ are isospectral. \\
%  It has the property that commute with the equilibrium Hamiltonian.

Consider the matrix $Q_{0}^{2L}$ defined in \eqref{Q0Exp}. All terms are diagonal except the last one. This last non-diagonal can be identified with the second Casimir of the $gl(N-1)$ subalgebra. We denote it by $\hat{C}_{2}^{N-1}$, i.e.

@@

We denote its eigenvalues by $C_{2}^{N-1}$. Since the configuration space of the process is given by the tensor product of the first fundamental representation of $gl(N)$, we can decompose it in a direct sum of irreducible representation of $gl(N)$. As a consequence, the Bethe states (that belong to the configurations space) can be written as a direct sum of vectors, each of them belonging to an irreducible representation of $gl(N)$. On these irreducible vectors $\hat{C}_{2}^{N-1}$ acts diagonally with eigenvalues $C_{2}^{N-1}$ given in terms of shifted weights, i.e. 

@@

\\&=N x^{2L+2}+2(N+1) x^{2L+1}+ \left(N+2m_1(m_N+1)-(N+2)(L-m_N)+2C_{2}^{N-1}\right)x^{2L}+\ldots
where we denote by 
	\Lambda_{\bm{m}}:=N+2m_1(m_N+1)-(N+2)(L-m_{N})+2C_{2}^{N-1}
the eigenvalues for arbitrary $\bm{m}$ of $Q_{0}^{2L}$. 

@@

\paragraph{Exchange relations between charges} Since, in general, the coefficients of the polynomial form of the elements of $U_{0}(x)$ and the charges do not commute, it is useful to find explicit exchange relations among them. Using \eqref{EX1}, \eqref{EX2}, \eqref{EX3}, \eqref{EX4},\eqref{EX5} and \eqref{EX6} we obtain:
	\item 
for every $i,j\in\{1,\ldots,N-1\}$ 

@@

\item  for $i,j,k\in\{1,\ldots,N-1\}$ such that $i\neq j\neq k\neq i,$

@@

Using the QISM results found in the previous subsections it is possible to rewrite $W$ in function of first non-trivial conserved charges of the system. Indeed, thanks to integrability

@@

Since $T(x)=\sum_{a=0}^{2L}Q^{2L}x^{a}$, the first non-diagonal charge $Q^{2L}$ commutes with $H^{''}$ and thus we can equivalently look for a matrix $W$ such that 
